---
output: github_document
---

<!-- README.md is generated from README.Rmd. Please edit that file -->

```{r, include = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>",
  fig.path = "man/figures/README-",
  out.width = "100%"
)
```

# drsurv

<!-- badges: start -->
<!-- badges: end -->

The goal of `drsurv` is to implement several doubly robust estimators for the 
    survival difference at a given time point and one more complex 
    doubly robust estimator for the survival curve process. The estimators 
    are doubly robust in the sense that they are consistent if the censoring 
    model is correctly specified for censoring and either the outcome model 
    is correctly specified for confounding or the exposure model is correctly 
    specified for confounding. See https://arxiv.org/abs/2310.16207 for 
    more details and examples. 

## Installation

You can install `drsurv` like so:

``` r
remotes::install_github("sachsmc/drsurv")
```

## Example

This is a basic example which shows you how to solve a common problem:

```{r example}
library(drsurv)
## basic example code

df <- rotterdam
df$time <- pmin(df$rtime, df$dtime) / 365.25
df$status <- ifelse(df$recur == 1 | df$death == 1, 1, 0)
df$censor <- 1 - df$status
drFit.sjovan <-
 sjovan_survdiff(
   oformula = Surv(time, status) ~ chemo + year + age + meno +
     size + factor(grade) + nodes + pgr + er + hormon,
   ofunc = "survreg",
   cformula = Surv(time, censor) ~ chemo + year + age,
   cfunc = "survreg",
   eformula = chemo ~ year + age + meno + size +
     factor(grade) + nodes + pgr + er + hormon,
   method = "DR",
   times = c(2.5, 5, 7.5),
   se.type = "sandwich",
   data = df
 )
drFit.sjovan
```

The other methods are `blanche_survdiff` and `pseudo_survdiff`.

